Exploratory Analysis Reece C

### 2025-12-04 Exploratory Analysis Reece C.Rmd
Working on graphs

---
title: "Exploratory Analysis"
author: "Reece Carmody"
date: "2025-11-17"
output: pdf_document
---

@@

@@

@@

cluster_plot = merged %>% 
  inner_join(df3, by = "Date")

# You can change the names to see different variables and their clusters
ggplot(merged, aes(x = cluster_plot[ , "mean_Turbidity"], y = cluster_plot[ , "Ferric.chloride..mg.L"], # you can compare any two columns
                   color = factor(cluster))) +
  geom_point() +
  labs(title = "K-Means Clustering", color = "Cluster") +
  theme_bw()

@@

>>>>

---
title: "Exploratory Analysis Reece C"
author: "Reece Carmody"
date: "2025-11-17"
output: pdf_document
---

@@

# Merging data

@@

# Clustering (probably not as useful with time series data...)

@@

full_merge = merged %>% 
  inner_join(df3, by = "Date")

# You can change the names to see different variables and their clusters
ggplot(full_merge, aes(x = full_merge[ , "mean_Turbidity"],
                       y = full_merge[ , "Ferric.chloride..mg.L"], # you can compare any two columns
                   color = factor(cluster))) +
  geom_point() +
  labs(title = "K-Means Clustering", color = "Cluster") +
  theme_bw()

@@

# Exploratory plots

long_df = full_merge %>%
  pivot_longer(cols = c("mean_Temp", "mean_pH", "mean_Conductivity", "mean_Turbidity",
                        "alkalinity", "hardness", "Ferric.chloride..mg.L", "Cationic.Polimer..mg.L"),
               names_to = "metric",
               values_to = "value")

ggplot(long_df, aes(x = Date, y = value))

ggplot(full_merge, aes(x = Date, y = mean_pH)) +
  geom_smooth() + 
  labs(title = "title") +
  theme_bw()
